% This is a custom resume created by Kyle Spencer <kylecspencer@gmail.com>. Feel free to 
% use / modify this for personal use.
%
% This requires XeTeX to compile because of the fontspec package. You must also chose a font that
% is installed on your system. I used Roboto Light, which is not installed by default on
% most systems.
%
% Enjoy!
% - Kyle Spencer
\documentclass[12pt]{article}

% Packages
\usepackage[margin=0.5in]{geometry}
\usepackage{ragged2e}
\usepackage{xcolor}
%\usepackage{fontspec}
\usepackage{enumitem}

\input{glyphtounicode}
\pdfgentounicode=1

% Section commands, used to make a pretty aligned title column with minipages

% Insert entire first minipage, taking text as parameter.
% Starts next multipage so content can begin immediatly after.
\newcommand{\startsec}[1]{
% BEGIN COMMAND
\noindent\begin{minipage}{0.15\linewidth}
\large #1
\end{minipage}%
\noindent\begin{minipage}{0.85\linewidth}
\begin{flushleft}
% END COMMAND
}

% Ends second minipage
\newcommand{\stopsec}{
% BEGIN COMMAND
\end{flushleft}
\end{minipage}
% END COMMAND
}

% Provides nice linebreak
\newcommand{\fullstop}{
\vskip\medskipamount % or other desired dimension
\leaders\vrule width \textwidth\vskip0.4pt % or other desired thickness
\vskip\medskipamount % ditto
\nointerlineskip
}

% Begin Content
\begin{document}

%Nice font, must be a system font.
%\setmainfont{Lato Light}

% No page numbering
\pagenumbering{gobble}

% Header - Name / Generic Info
\begin{center}
\LARGE Kyle Spencer
\break
\normalsize
State College, Pennsylvania, United States
\break
\small kylecspencer@gmail.com | www.kylespencer.me | 412-759-1172 | github.com/kylecs
\end{center}

\fullstop

% Education Section
\startsec{\textbf{Education}}
\textbf{The Pennsylvania State University}
\smallskip
\begin{itemize}[noitemsep,nolistsep]
  \item BS in Computer Science, Spring 2019 (Expected)
  \item Minor in Mathematics
  \item 3.71 GPA, 3.97 Major GPA
  \item Dean's List Multiple Semesters
\end{itemize}
\stopsec
% End Education Section

\fullstop

% Experience Section
\startsec{\textbf{Experience}}

\textbf{Penn State Beaver}\textit{, Computer Science Tutor}
\hfill
\small
(September 2016 - December 2016)
\medskip
\begin{itemize}[noitemsep,nolistsep]
  \item Taught fundamentals of computer science and C++ to students.
  \item Assisted students with projects and assignments.

\end{itemize}
\normalsize
\medskip

\textbf{Penn State Beaver Library}
\hfill
\small
(May 2016 - August 2016)
\medskip
\break
Built a dynamic catalog website showing all DVDs available for borrow, providing
an interface for browsing, searching, sorting, and adding DVDs.
\medskip
\begin{itemize}[noitemsep,nolistsep]
  \item Used Node.js with Express and Postgres to implement the backend of the website which was deployed to OpenShift Cloud Hosting.
  \item Designed a single-page frontend with Angular.js and Bootstrap that asynchronously requested data from the backend server.
  \item Implemented a cache-based solution with node-cache to ensure fresh data for the primary pages always loaded quickly.

\end{itemize}
\normalsize
\medskip
\textbf{Penn State Beaver Library}
\hfill
\small
(May 2015 - August 2015)
\medskip
\break
Created a dynamically generated and categorized showcase wordpress website for the science fiction books available at the
Penn State libraries.
\medskip
\begin{itemize}[noitemsep,nolistsep]
  \item Implemented a Java program with Selenium that downloaded relevant book identifiers from the Penn State Library
website, then used the Goodreads API to acquire more book data.
  \item Created program that formatted the book data into HTML book pages and category pages, then uploaded it to the wordpress website automatically using Selenium.
\end{itemize}
\normalsize
\stopsec
% End Experience Section

\fullstop

% Start Projects Section
\startsec{\textbf{Projects}}
\textbf{HTTP Server}
\small
\smallskip
\begin{itemize}[noitemsep,nolistsep]
  \item Implemented an HTTP/1.1 server in Rust, with support for serving static websites.
\end{itemize}
\normalsize

\medskip
\textbf{Kernel}
\small
\smallskip
\begin{itemize}[noitemsep,nolistsep]
  \item Created a text-based x86 kernel with C and IA-32 Assembly.
  \item Implemented a terminal driver, a keyboard driver, a PCI driver, and a basic command interface.
\end{itemize}
\normalsize

\medskip
\textbf{NASA Image API Timelapse}
\small
\smallskip
\begin{itemize}[noitemsep,nolistsep]
  \item Wrote a script with Python to generate an overhead view timelapse GIF of anywhere on earth given the coordinates
  using NASA's Earth Image API and ImageMagick.
 % \item Implemented functionality to access NASA's Earth Image API and download chronological images, then use ImageMagick to %automatically generate the GIF.
\end{itemize}
\normalsize

\medskip
\textbf{Dynamic Forum Website}
\small
\smallskip
\begin{itemize}[noitemsep,nolistsep]
  \item Used Python with Flask to create a customizable forum website, with support for user accounts, posts, comments, and a dynamic subforum hierarchy.
\end{itemize}
\normalsize

\medskip
\footnotesize
% View more at github.com/kylecs
\normalsize
\stopsec
% End Projects Section

\fullstop

% Start Skills Section
\startsec{\textbf{Skills}}
\small
\textbf{Proficient:}	C++, Java
\break
\textbf{Skilled:} JavaScript, Python, C, MIPS
\break
\textbf{Concepts:} Full Stack Web Development, Relational Databases, SQL, REST APIs, Cloud Platforms, Object Oriented Programming, Concurrent Programming, Systems Programming
\break
\textbf{Tools | Libraries:} Linux, Git, Angular.js, Node.js, Flask, Bootstrap
% Other: Linux, Git, Full Stack Web Development, Systems Programming, Angular.js, Node.js, REST
\stopsec
% End Skills Section

% We did it!
\end{document}
